No Title

### 2017-10-27 paper/paper.tex
new plots

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We find that the satellites in MW show a distribution significantly
thinner and flattened compared to the expectaions of a random
spherical distribution and simulations based on the Lambda Cold Dark
Matter paradigm.
In turn, M31 is completely consistent with the expectations from a
spherical satellite distribution and LCDM simulations.
The satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. None of the pairs in the simulation show
a similar degree of alignment. 
However, the simulations are consistent with a random uniform
distribution, making the result from the observations consistent with
these theoretical expectations.
This special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the cosmological context provided by
simulations. 
We summarize these results in a simple multivariate Gaussian
model to estimate that only $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality. 
\end{abstract}

@@

\section{Local Group Satellites in the Illustris Simulation}
\label{sec:NumericalSetup}

@@

We find 27 pairs with these conditions. We show in the Appendix A the
physical  properties (stellar masses, maximum circular velocities,
radial velocities and separation) in those pairs. 
We then select the pairs where in both halos there are at least 15
detected subhalos. 
We end up with a total of 20 pairs that fulfill these criteria.

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_width.pdf}
\caption{Plane width characterization in the Local Group and the
  Isolated Pairs. In all panels the horizontal axis corresponds to the
  M31 or the most massive halo in the pair and the vertical axis to
  the MW or the least massive halo in the pair.
The panel on the left shows the plane width in physical units
comparing the results of five measurements from the observations
(stars) and the result of spherically randomizing the satellite
positions (circles). 
The panel in the middle compares the average from the observations
(star) and the average from each one of the Isolated Pairs (circles
with error bars).
The panel on the right has the same information as the middle panel,
only that this time each point has been normalized (median substracted
and normalized by the standar deviation) to the results of its
randomization. 
The main message of this series of plots is that the MW has a
significantly thiner plane both compared to the result of its own
satellite spherical randomization (left panel) and the expectation from
simulations (middle panel). 
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In the M31 their satellites are in agreement with the expectations
both from an spherical distribution and the results form the
simulations. 
A second conclusion is that the spherically averaged plane width
MW (seen in the point cloud in the left panel) is smaller than the
average expectation from simulations, while for M31 the spherical
average is consistent with simulations. 
\label{fig:scatter_width}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The message holds in this case as for the plane width.
The MW is has a significantly low $c/a$ value compared to the
expectation from a spherical distribution and simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
M31 is consistent both with an spherical distribution and the results
from simulations.
However, in this case the axis ratio in the spherically averaged case
is completeley consistent with the expectation from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently this result is outside the expectations from the
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances $\mu\approx 1$ is as likely as
any other value.
\label{fig:scatter_mu}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper/lower row summarizes the results for M31/M31.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}

@@

@@

@@

>>>>

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We use the Illustris-1 and ELVIS simulations to show that the
MW satellite distribution is significantly thinner and more oblate
than the expectations from the Lambda Cold Dark Matter (LCDM)
paradigm. In contrast, the satellites in M31 are fully consistent with the
average expectations from simulations.
We also find that the satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. While none of the pairs in the simulations show
a similar degree of alignment, these alignments are consistent with a
random uniform distribution, making the result from the observations
consistent with these theoretical expectations.
The special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the cosmological context provided by
LCDM simulations. 
We estimate that only $0.5\%$ to $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier in a sample of simulated galaxy pairs.
\end{abstract}

@@

\section{Data from the ELVIS simulation}
\label{sim:ELVIS}

\section{Data from the Illustris Simulation}
\label{sec:illustris}

@@

We find 27 pairs with these conditions. 
We then select the pairs where in both halos there are at least 15
detected subhalos, thus discarding pairs with halos with the lowest
mass.
We end up with a total of 20 pairs that fulfill these criteria,
Appendix A shows the physical  properties (stellar masses, maximum
circular velocities, radial velocities and separation) in those pairs.

@@

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
\caption{Plane width characterization in the Local Group and the
  Isolated Pairs. In all panels the horizontal axis corresponds to the
  M31 or the most massive halo in the pair and the vertical axis to
  the MW or the least massive halo in the pair.
The panel on the left shows the plane width in physical units
comparing the results of five measurements from the observations
(stars) and the result of spherically randomizing the satellite
positions (circles). 
The panel in the middle compares the average from the observations
(star) and the average from each one of the Isolated Pairs (circles
with error bars).
The panel on the right has the same information as the middle panel,
only that this time each point has been normalized (median substracted
and normalized by the standar deviation) to the results of its
randomization. 
The main message of this series of plots is that the MW has a
significantly thiner plane both compared to the result of its own
satellite spherical randomization (left panel) and the expectation from
simulations (middle panel). 
This low value is $2\sigma$ away from what is expected in a spherical
distribution. 
In the M31 their satellites are in agreement with the expectations
both from an spherical distribution and the results form the
simulations. 
A second conclusion is that the spherically averaged plane width
MW (seen in the point cloud in the left panel) is smaller than the
average expectation from simulations, while for M31 the spherical
average is consistent with simulations. 
\label{fig:scatter_width}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The message holds in this case as for the plane width.
The MW is has a significantly low $c/a$ value compared to the
expectation from a spherical distribution and simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
M31 is consistent both with an spherical distribution and the results
from simulations.
However, in this case the axis ratio in the spherically averaged case
is completeley consistent with the expectation from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_mu.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for $\mu$ the absolute value of the dot product between the
vector connecting the main galaxies and the vector perpendicular to
the satellite plane.
In this case both the MW and M31 show a strong alignment.
Apparently this result is outside the expectations from the
simulations and atypical compared to the spherical results. 
However, this is not the case. The $\mu$ distributions in the
randomization and the simulation are consistent with a uniform
distribution.
Under such circumstances $\mu\approx 1$ is as likely as
any other value.
\label{fig:scatter_mu}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_illustris_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper/lower row summarizes the results for M31/M31.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}

@@

\subsection{$c/a$ axis ratio}

\subsection{$b/a$ axis ratio}

\subsection{s}

@@

\section{Discussion}
\subsection{Gaussian Model}

\begin{equation*}
\begin{bmatrix}
1.6  & 1.2 & 7.3\times10^{-1} & 7.9\times 10^{-2} & 1.0\times 10^{-1}
& 6.5\times 10^{-2}\\
 1.2  & 1.2 & 3.5\times10^{-1} & 8.9\times 10^{-3} & 1.5\times 10^{-2} &-7.4\times10^{-2}\\
 7.3\times10^{-1} & 3.5\times10^{-1} & 0.668 & 0.102 &-0.00331 & 0.151\\
 7.9\times 10^{-2}  & 8.9\times 10^{-3} & 0.102 & 0.474   & 0.695 &-0.127\\
 1.0\times 10^{-1}  & 1.5\times 10^{-2} &-0.003  &0.695  &1.48 &-0.695\\
 6.5\times 10^{-2} & -7.4\times10^{-2} & 0.151 &-0.127 &-0.695 & 0.607
\end{bmatrix}
\end{equation*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_width.pdf}\\
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}\\
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}\\
\includegraphics[width=0.30\textwidth]{scatter_ranked_elvis_mu.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_elvis_mu.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_M31.pdf}
\includegraphics[width=0.45\textwidth]{gaussian_model_elvis_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper/lower row summarizes the results for M31/M31.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}
